The problem and promise of scale in multilayer networks

### 2019-12-09 paper/introduction.Rmd
a bit of case study
fin pour la nuit

<!-- ### Social proximity scale 
sociality exists 
-->
Sociality is important because conspecifics have positive and negative benefits

Sociality is accompanied by positive and negative effects, and evolves when the net benefit is greater than the cost [@silk2007]. Positive effects include protection from predators, mating opportunities, and resource location and access [@silk2007]. Negative effects include increased competition, risk of disease transfer and infection [@silk2007].

@@

<!-- ### Case study 
deer
fogo caribou
-->

>>>>

<!-- ### Social proximity scale 
sociality exists 
-->

<!-- Sociality exists across scales -->

<!-- How do consider shared space use -->

<!-- Spatial proximity as a proxy for interactions  -->

<!-- Social association -->

<!-- Home range overlap  -->

<!-- Connection of individuals within a social structure can be formalized/analyzed as a social network -->

co-occurrence is used in social network studies as a synonym for social association (Farine and Whitehead 2015).

Sociality, defined simply as some degree of shared space use among conspecifics [@tinbergen1951], exists across scales. Social scale is the type of social relationship observed and how this relationship is defined [@farine2015]. For example, grooming and mating relationships require immediate proximity between conspecifics whereas home range overlap occurs over much larger spatial and temporal scales.

Shared space is a requirement for social interaction, however, it remains unclear whether spatial proximity scales predictably with social interactions (Castles et al. 2014; Farine 2015).

<!-- Sociality is defined here as by @tinbergen1951: "an animal is called social when it strives to be in the neighbourhood of fellow members of its species when performing some, or all, of its instinctive activities". -->

<!-- Sociality is important because conspecifics have positive and negative benefits -->

<!-- Sociality is accompanied by positive and negative effects, and evolves when the net benefit is greater than the cost [@silk2007]. Positive effects include protection from predators, mating opportunities, and resource location and access [@silk2007]. Negative effects include increased competition, risk of disease transfer and infection [@silk2007]. -->

@@

<!-- ### Case study 
deer
fogo caribou
-->
We will use two case studies to explore the sensitivity of multilayer network measures across scales. One, using an island population of caribou (*Rangifer tarandus*)
